|

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
docs(manuscript): lint
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

@@

Extension of @fig-model-results, Pyro&thinsp;-Velocity (Model 2) outperforms scVelo on
PBMC and pancreas datasets. Same format as in @fig-model-results and
@suppfig-model-results
:::

@@

Extension of @fig-lineage-tracing presenting an extended comparison of
Pyro&thinsp;-Velocity and scVelo on scRNA-seq datasets with lineage barcoding
information (LARRY dataset). a. uni-fate Monocyte lineage analysis with
Pyro&thinsp;-Velocity Model 2, b. uni-fate Neutrophil lineage analysis with
Pyro&thinsp;-Velocity Model 2, c. Neutrophil and Monocyte bi-fate lineage analysis with
Pyro&thinsp;-Velocity Model 1, and d. multi-fate lineage analysis with Pyro&thinsp;-Velocity
Model 1. The panel descriptions are the same as in @fig-lineage-tracing
:::

>>>>

# Competing financial interests statement

L.P. has financial interests in Edilytics, Inc., Excelsior Genomics, and SeQure
Dx, Inc. L.P.’s interests were reviewed and are managed by Massachusetts General
Hospital and Partners HealthCare in accordance with their conflict of interest
policies.

@@

Extension of @fig-model-results, Pyro&thinsp;-Velocity (Model 2) outperforms
scVelo on PBMC and pancreas datasets. Same format as in @fig-model-results and
@suppfig-model-results.
:::

@@

Extension of [@fig-lineage-tracing] presenting an extended comparison of
Pyro&thinsp;-Velocity and scVelo on scRNA-seq datasets with lineage barcoding
information (LARRY dataset). a. uni-fate Monocyte lineage analysis with
Pyro&thinsp;-Velocity Model 2, b. uni-fate Neutrophil lineage analysis with
Pyro&thinsp;-Velocity Model 2, c. Neutrophil and Monocyte bi-fate lineage
analysis with Pyro&thinsp;-Velocity Model 1, and d. multi-fate lineage analysis
with Pyro&thinsp;-Velocity Model 1. The panel descriptions are the same as in
[@fig-lineage-tracing].
:::
